---
title: "test demo"
author: "Mohamad Elian"
date: today
execute: 
  echo: false
knitr:
  opts_chunk: 
    warning: false
    message: false
format:
  html:
    toc: true
    page-layout: full
    css: style.scss
params:
  hom: true
  het: true
  substate: true
  vcf: true
  type: ''
  minsnp: 0
  indiv: 0

---

```{r state}

hom <- params$hom
het <- params$het
substate <- params$substate
vcfstate <- params$vcf
type <- params$type
minsnp <- params$minsnp
cutoff <- params$indiv
```

<!--These are the files that will be sources -->
```{r load-everything}

homfile <- "HOM_temp.tsv"
hetfile <- "HET_temp.tsv"
indiv_homfile <- "HOM.indiv"
indiv_hetfile <- "HET.indiv"
vcf_info <- "vcf_info.txt"
bedfile <- "genes.bed"
HOMisland <- "HOM_topsnps.tsv"
HETisland <- "HET_topsnps.tsv"

source("test.R", local = knitr::knit_global())

```

```{r setup-packages}
#| include: false
#| fig-cap: ""
plotly::plot_ly()
DT::datatable(data.frame())
```

:::{.column-margin}
Input Information:
```{r set-margins}
#| eval: !expr vcfstate
#| results: asis

knitr::kable(side_info) %>%
  kable_styling(bootstrap_options = "bordered")

```
:::

## Individual information

This table provides information about the individuals in the dataset, including the number of ROH and/or HRR segments, as well as the total length of these segments. This information can be useful for understanding the overall level of homozygosity and heterozygosity in the population, as well as for identifying individuals that may be of particular interest for further analysis.

::: {#tbl-indiv .mb-large}
```{r indiv-info}
#| eval: true
#| results: asis

if (hom && het) {
  cat("::: {.panel-tabset}\n\n")
}

if (hom) {
  if (hom && het) cat("## ROH\n\n")
  print(htmltools::tagList(
    datatable(indiv_HOM, rownames = FALSE, class = 'cell-border stripe') %>%
      formatStyle(columns = colnames(indiv_HOM), fontSize = '80%')
  ))
}

if (het) {
  if (hom && het) cat("\n## HRR\n\n")
  print(htmltools::tagList(
    datatable(indiv_HET, rownames = FALSE, class = 'cell-border stripe') %>%
      formatStyle(columns = colnames(indiv_HET), fontSize = '80%')
  ))
}

if (hom && het) cat("\n:::\n\n")
```
Individual information

:::

## PLOTS

This plot shows the number of ROH and/or HRR segments that overlap with a certain number of genes. This information can be useful for understanding the distribution of ROH and/or HRR segments across the genome, as well as for identifying regions of the genome that may be particularly enriched for these segments.

::: {#fig-roh .mb-large}

```{r fig-roh}
#| results: asis

if (hom && het) {
  cat("::: {.panel-tabset}\n\n")
}

make_plot <- function(df, ylab) {
  print(htmltools::tagList(
    plot_ly(df, x = ~gene_count, y = ~n, type = "bar") %>%
      layout(xaxis = list(title = "number of Genes"),
             yaxis = list(title = ylab))
  ))
}

if (hom) {
  if (hom && het) cat("## ROH\n\n")
  make_plot(num_genes_HOM, "number of ROH")
}

if (het) {
  if (hom && het) cat("\n## HRR\n\n")
  make_plot(num_genes_HET, "number of HRR")
}

if (hom && het) cat("\n:::\n\n")
```
nROH vs Genes

:::

This is some comment, see @fig-roh

## TABLES
This table shows the longest ROH and/or HRR in the genome alongside identifying information for these segments. This information can be useful for understanding the characteristics of the longest ROH and/or HRR segments in the dataset, as well as for identifying specific regions of the genome that may be of particular interest for further analysis.

::: {#tbl-roh .mb-large}
```{r tbl-roh}
#| eval: true
#| results: asis

if (hom && het) {
  cat("::: {.panel-tabset}\n\n")
}

if (hom) {
  if (hom && het) cat("## ROH\n\n")
  print(htmltools::tagList(
    datatable(plot_table_HOM, rownames = FALSE, class = 'cell-border stripe') %>%
      formatStyle(columns = colnames(plot_table_HOM), fontSize = '80%')
  ))
}

if (het) {
  if (hom && het) cat("\n## HRR\n\n")
  print(htmltools::tagList(
    datatable(plot_table_HET, rownames = FALSE, class = 'cell-border stripe') %>%
      formatStyle(columns = colnames(plot_table_HET), fontSize = '80%')
  ))
}

if (hom && het) cat("\n:::\n\n")
```
Table caption

:::

This text references table @tbl-roh

## Islands
The below tables show the ROH and HRR islands as defined by the Chessari et al. In this context, an island is defined as an ROH/HRR which contains at least 4 of the top 0.1% of SNPs from the dataset. The islands are identified using the topsnp.py script, which takes in the counts of SNPs in ROH/HRR segments and identifies the top SNPs in either p-value or quantile mode. in this case `r type`

::: {#tbl-island .mb-large}
```{r tbl-island}
#| eval: true
#| results: asis

if (hom && het) {
  cat("::: {.panel-tabset}\n\n")
}

if (hom) {
  if (hom && het) cat("## ROH\n\n")
  print(htmltools::tagList(
    datatable(plot_ROHislands, rownames = FALSE, class = 'cell-border stripe') %>%
      formatStyle(columns = colnames(plot_table_HOM), fontSize = '80%')
  ))
}

if (het) {
  if (hom && het) cat("\n## HRR\n\n")
  print(htmltools::tagList(
    datatable(plot_HRRislands, rownames = FALSE, class = 'cell-border stripe') %>%
      formatStyle(columns = colnames(plot_table_HET), fontSize = '80%')
  ))
}

if (hom && het) cat("\n:::\n\n")

```
ROH and HRR islands

:::

This is the description of @tbl-island

## Two figures 

This figure shows the length distribution and the numbe rof SNPs found in each ROH and/or HRR segment across the genome. 

::: {#fig-dot .column-page}

```{r fig-dot}
#| results: asis

if (hom && het) {
  cat("::: {.panel-tabset}\n\n")
}

make_plots <- function(df, xlab, kval) {
  p1 <- plot_ly(df, x = ~ROH_num, y = ~y1_kb, type = "scatter") %>%
    layout(xaxis = list(title = xlab),
           yaxis = list(title = paste0("length KB (K = ", kval, ")")))
  
  p2 <- plot_ly(df, x = ~ROH_num, y = ~y1_nsnp, type = "scatter", mode = "markers",
        marker = list(color = "red")) %>%
    layout(xaxis = list(title = xlab),
           yaxis = list(title = paste0("number of SNP (K = ", kval, ")")))
  
  print(htmltools::tagList(subplot(p1, p2, nrows = 1, shareX = FALSE, shareY = FALSE, titleX = TRUE, titleY = TRUE, margin = 0.04)))
}

if (hom) {
  if (hom && het) { cat("## ROH\n\n") }
  make_plots(ROH_info_HOM, "ROH number", khom)
}

if (het) {
  if (hom && het) { cat("\n## HRR\n\n") }
  make_plots(ROH_info_HET, "HRR number", khet)
}

if (hom && het) cat("\n:::\n\n")

```
Length and number of ROH and/or HRR segments
:::

I am referencing @fig-dot. More specifically

## Gene Based Outlook

Using the gene annotation file provided by the user, this table shows the number of ROH and/or HRR segments that overlap with a certain number of genes. This information can be useful for understanding the distribution of ROH and/or HRR segments across the genome, as well as for identifying regions of the genome that may be particularly enriched for these segments.

::: {#tbl-gene .mb-large}

```{r tbl-gene}
#| eval: true
#| results: asis

if (hom && het) {
  cat("::: {.panel-tabset}\n\n")
}

if (hom) {
  if (hom && het) cat("## ROH\n\n")
  print(htmltools::tagList(
    datatable(final_ROH_count, rownames = FALSE, class = 'cell-border stripe') %>%
      formatStyle(columns = colnames(final_ROH_count), fontSize = '80%')
  ))
}

if (het) {
  if (hom && het) cat("\n## HRR\n\n")
  print(htmltools::tagList(
    datatable(final_HRR_count, rownames = FALSE, class = 'cell-border stripe') %>%
      formatStyle(columns = colnames(final_HRR_count), fontSize = '80%')
  ))
}

if (hom && het) cat("\n:::\n\n")
```
Gene table caption

:::

<!--The following codeblocks will run if subpopulations are being used -->
```{r load-subpop}
#| eval: !expr substate
#| results: asis

subpop <- "subfile.tsv"
source("subpopulations.R", local = knitr::knit_global())
```

<!--This is for the subpop nroh table -->
```{r tbl-subpop}
#| eval: !expr substate
#| results: asis

cat("## Subpopulations\n\nSome text about the subpopulation\n\n")
cat("### samples per subpopulation\n\n")
cat("::: {#tbl-subpop .mb-large}\n\n")

print(htmltools::tagList(
  datatable(num_samples_df, rownames = FALSE, class = 'cell-border stripe') %>%
    formatStyle(columns = colnames(num_samples_df), fontSize = '80%')
  ))

cat("\nTable caption\n\n:::\n")
cat("This is the caption and we will reference @tbl-subpop\n")
```

<!--This is for the number of ROH/HRR per subpopulation figure -->
```{r fig-subpopnroh}
#| eval: !expr substate
#| results: asis

cat("### ROH per subpopulation\n\n")
cat("::: {#fig-subpopnroh .mb-large}\n\n")

if (hom && het) {
  cat("::: {.panel-tabset}\n\n")
}

make_plot <- function(df, ylab) {
  print(htmltools::tagList(
    plot_ly(df, x = ~groupings, y = ~NSEG,color = ~groupings,
            split = ~groupings, type = "box", box = list(
              visible = T), meanline = list(visible = T)) %>%
      layout(xaxis = list(title = "subpopulation"), yaxis = list(title = ylab)))
    )
}



if (hom) {
  if (hom && het) { cat("## ROH\n\n") }
  make_plot(plot_nROH, "nROH (KB)")
}

if (het) {
  if (hom && het) { cat("\n## HRR\n\n") }
  make_plot(plot_nHRR, "nHRR (KB)")
}

if (hom && het) cat("\n:::\n\n")
cat("This is my caption\n:::\n\n")
cat("I am now writing some stuff about @fig-subpopnroh")

```

<!--This is for the length of ROH per subpopulation -->
```{r fig-subpoplroh}
#| eval: !expr substate
#| results: asis

cat("### ROH/HRR length per subpopulation\n\n")
cat("::: {#fig-subpoplroh .mb-large}\n\n")

if (hom && het) {
  cat("::: {.panel-tabset}\n\n")
}

make_plot <- function(df, ylab) {
  print(htmltools::tagList(
    plot_ly(df, x = ~groupings, y = ~KBAVG,color = ~groupings,
            split = ~groupings, type = "box", box = list(
              visible = T), meanline = list(visible = T)) %>%
      layout(xaxis = list(title = "subpopulation"), yaxis = list(title = ylab)))
    )
}



if (hom) {
  if (hom && het) { cat("## ROH\n\n") }
  make_plot(plot_violin_ROH, "Length of ROH (KB)")
}

if (het) {
  if (hom && het) { cat("\n## HRR\n\n") }
  make_plot(plot_violin_HRR, "Length of HRR (KB)")
}

if (hom && het) cat("\n:::\n\n")
cat("This is my caption\n:::\n\n")
cat("I am now writing some stuff about @fig-subpoplroh")
```